Brownian Dynein Model

### 2015-07-29 latex/derivation.tex

@@

>>>>

This system is solved via Mathematica...\\

@@

\begin{align}
  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
  \left(B_1 - \frac{B_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(B_2 - \frac{B_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{B_4}{D_4}X_4\\
  \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + 
		\frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + 
		\left(B_3 - \frac{B_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
\end{align}

\begin{align}
  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
 \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
\end{align}

\begin{multline}
  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 =
		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
\end{multline}
\begin{multline}
 \hspace*{-2cm}\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 = \\
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right) \\
\end{multline}
\begin{align}
  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4 \\
\end{align}

\begin{multline}
  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
  \frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)\dot{\Theta}_{bl} + \\
		0 + 0 + 0 =
		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\\
\end{multline}
\begin{align}
  \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4
\end{align}

\begin{multline}
  \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} = \\
		\frac{\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)}
		{\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)} * \\
		\left(X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\right)
\end{multline}
\begin{align}
  \hspace*{-2cm}\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\dot{\Theta}_{bl} +
		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} + 0 + 0 &=
		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) \\
  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4
\end{align}

\begin{multline}
  \hspace*{-2cm}\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
  \frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)\dot{\Theta}_{bl} = \\
		X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\\
\end{multline}
\begin{multline}
		\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)\dot{\Theta}_{ml} =
		X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -\\
		\frac{\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)}
		{\left(A_1 - \frac{A_4D_1}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right) - 
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left(B_1 - \frac{B_4D_1}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_1 - \frac{C_4D_1}{D_4}\right)\right)\right)} * \\
		\left(X_1 - \frac{A_4}{D_4}X_4 - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right) -
		\frac{\left(A_2 - \frac{A_4D_2}{D_4} - \frac{\left(A_3 - \frac{A_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		{\left(B_2 - \frac{B_4D_2}{D_4} - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(C_2 - \frac{C_4D_2}{D_4}\right)\right)}
		\left( X_1 - \frac{B_4}{D_4}X_4 - \frac{\left(B_3 - \frac{B_4D_3}{D_4}\right)}{\left(C_3 - \frac{C_4D_3}{D_4}\right)}\left(X_1 - \frac{C_4}{D_4}X_4\right)\right)\right)
\end{multline}
\begin{align}
  \left(C_1 - \frac{C_4D_1}{D_4}\right)\dot{\Theta}_{bl} + \left(C_2 - \frac{C_4D_2}{D_4}\right)\dot{\Theta}_{ml} + \left(C_3 - \frac{C_4D_3}{D_4}\right)\dot{\Theta}_{mr} + 0 &= X_1 - \frac{C_4}{D_4}X_4\\
  D_1\dot{\Theta}_{bl} + D_2 \dot{\Theta}_{ml} + D_3 \dot{\Theta}_{mr} + D_4 \dot{\Theta}_{br} &= X_4
\end{align}
